\section{IMPACT} %4 pages
\label{sec:impact}
\subsection{Potential for acquiring competencies during the fellowship to improve the prospects of 
reaching and/or reinforcing a position of professional maturity, diversity and independence, 
in particular through exposure to transferable skills training}
% \begin{itemize}
% \item People Management training skills = supervision of people / students / PhD students. 
% \item Budget Administration = knowing how to use a budget. Learning by doing with the project budget at Berkeley and at TUM.
% \item Intellectual property Rights training = follow courses in US and in Germany.
% \item Business acumen. How to create a company = 2 courses with UnternehmerTUM for scientists back at TUM in Year 3.
% \item Possibly another People Management course to follow at TUM in Year 3 with the Life-long learning support unit scheme (people management course for University staff).
% \item How to write a grant = Course to follow back at TUM.
% \end{itemize}
The applicant has demonstrated in the past his ability
to acquire new knowledge after switching to a different research field
and  a  new  group.  Although  his  studies  were  in  the  electrical
engineering field,  he very easily integrated and  undertook a project
in  a  new  group   conducting  research  in  personal  robotics.  The
researcher's ability to  acquire new knowledge was evident  in terms of
the  different  scientific fields  and  application  domains he  could
easily  adopt  himself  (e.g.  3D  perception,  machine  learning  and
formal logical systems). Assets,  which  show the  high  potential of  the
applicant  to  acquire  new  knowledge  and  use  this  knowledge  for
conducting   high   level  research,   modeling   novel  systems   and
guiding/proposing novel applications. In this respect, at the outgoing
host  institution, he  will also  have  the potential  to acquire  new
knowledge and skills. Specifically, he will have the possibility to be
exposed to new tools and  methods, such as apprentice learning schema,
perception  of   deformable  objects, LQG-based motion planning, etc.  
Potential   collaborations  and interaction with the many excelling  robotic groups in the area around
Berkeley will also expand the applicants scientific horizons.
 
The capacity  of the applicant  to acquire new scientific  knowledge, his
future teaching  duties ) and the  complementary and
transferable courses (described in~\ref{sec:trans_skills}) he will follow, 
will allow him to be  ready for a  bright academic career with  leadership capacities
and solid business acumen.
 
He  will  after  three  years  also  have  learned  to  manage  rather
independent a first larger R\&D budget.
 
\subsection{Contribution to career development or re-establishment, where relevant}
The benefits of the proposed training period at Berkeley from a mid/long-term perspective will 
be essential. It will provide for continuity in the career of the applicant, and will allow for the consolidation and 
widening of his career prospects. All skills obtained during the \ksem\ project, ranging 
from computational, methodological, communicative, and collaborative together with 
teaching and mentoring, will allow him to achieve professional maturity and to become an 
independent researcher in his area of interest. Not to mention the extremely beneficial 
outcomes of the applicant's stay in a highly advanced and excelling educational  and 
research environment. A stay is expected to boost his academic skills and enhance his career development.

\subsection{Potential for creating long term collaborations and mutually beneficial cooperation between 
Europe and the Other Third Country} 
As a member of TUM and Berkeley, the applicant  will endeavor to contribute to create long-term
fruitful  collaborations  between  Berkeley and TUM through  a triple strategy 
agreed between the applicant, the IAS  leader Prof.  Beetz and the  TUM Department  
of  Computer Sciences:\\
\emph{Exchanges  of students  up  to  Master level}\\  
Study  Projects will  be planned in common between TUM and  Berkeley
(starting  from  applicant's  former   research  group)  mentors  and  mentored
students.  Short training  periods will  be planned  on both  sides to
execute these  projects, completed  by a common  \textbf{summer school}  in the
second  year  including all  hands-on  workshops, poster  competition,
invited  internationally  well-known   speakers  of  the  field.   TUM
students will benefit  from travel bursaries to be  applied from usual
German  sources  (DAAD,   Alexander  von  Humboldt  Foundation,  Bosch
Foundation, etc). 
% A duty of  the newly recruited staff is to maintain
% a small database of potential grant possibilities to support this very
% relation. 
The applicant will be supported  by the TUM-Forte office to identify the
best  funding  sources,  and    will  oversee  the  quality  of  the
applications written by the students.  This shall ensure a pipeline of
regular  financially  supported  student   projects  at  the  core  of
long-term  exchanges  with   Berkeley. Berkeley  students will equally  apply to
their usual funding bodies to finance study travel abroad.  Both TUM and
Berkeley students  will be  requested on
their return  to report on  their experiences abroad to  their mentors
and to the new students (both technologically and concerning the daily
life).   The  existing  TUM  Master  Program  \textbf{Robotics,  Cognition,
Intelligence}~\footnote{\url{http://www.in.tum.de/fuer-studieninteressierte/master-studiengaenge/robotics-cognition-intelligence.html}}, 
shall  be the  pipeline of exchanges,  and it  will be
steady  enough after  the conclusion  of applicant's  fellowship.  Thanks  to applicant's
professional and  personal experience, applicant will be  a successful example
and  a role  model for  young TUM/Berkeley  students /  PhD  students showing
scientific  and mobility  achievements. One  of applicant's  main contributions
will be to raise  the awareness for the program in the  US and to help
in recruiting more US graduate students.\\
\emph{Expected results:}\\
 3 students exchanged between Berkeley and TUM during
the period of  applicant's fellowship; up to 5 students  in the following five
years after the completion of the IOF contract. A summer school during
the  second year  (either in  Munich or at Berkeley)  with up  to 50
participants. \\  
\emph{Exchanges of  scientists from  PhD student  level to
post-doc and  senior scientists}\\
 The German Research  Foundation (DFG) offers  a multitude  of  programs to  sustain  research exchanges  and
collaboration with the US,  and complements nicely other programs from
foundations  for  the  same  purpose  (DAAD,  Alexander  von  Humboldt
Foundation, Bosch Foundation, etc). During  the period at TUM and Berkeley, 
Mr. Pangercic will help to connect principal  investigators of both institutions in order
to win  additional resources  to sustain the  flow of  activities with
University  of California in  Berkeley. In  order to  do that,  he will
exploit the  potentials of  the well-organized offices  network at
TUM, which  will help him at  three levels: a) by  the TUM-Forte office
concerning the  non-scientific parts of the projects  to be submitted;
b)  by the  IAS Chair  administration and  the TUM  Computer Sciences
Financial  Department   concerning  the  financial   details  of  such
proposals;  c)  by  the  TUM  Legal Office  (in  particular  regarding
Intellectual Property Rights  - IPR). Applicant's role will  then remain in the
frame of  scientific exchanges developments,  while the administrative
burden  will be taken  by these  three supporting  services.\\
\emph{Expected results:}\\
\begin{itemize}
\item Up  to 3  PhD students, 1  post-docs and 1  senior scientists
from  each side  performing research  training or  experiments  in the
corresponding   Berkeley   or   TUM laboratories.  
\item 1 common research projects developed in the first year;
1 common research project (eventually with other partners) financed in
the second year. Clarity of IPR.  
\item Another possibility - however highly competitive  - for  projects developed
in  common will  be to  insert research  teams from  Berkeley  into FP7
European Research proposals, with a request  to the NSF, or the NIH to
finance the US part.   
\item Ideally, high-level scientific publications can
be  acknowledged  as part  of  this  collaboration in  internationally
significant   peer-review   journals.  A   common   patent  with   its
exploitation  plan would  also  show the  success  of this  privileged
scientific pipeline  between University of California  in Berkeley and
TUM.
\end{itemize}
\emph{Cultural  and corporate understanding}\\
The socialization  part is a
key point  of this plan  and cultural awareness  will be part  of each
proposed  project. This cultural  awareness will  be acquired  on both
sides by  ensuring that  students and scientist  have time  during the
exchanges   to  visit  important   historical  areas,   eventually  be
accommodated  by locals  (especially  for the  students), be  proposed
German and English courses. This  cultural knowledge will be linked to
the visit  of main industrial  sites to approach nearer  the different
industrial cultures (for some of the students it will be an additional
opportunity  to  stay   longer  by  identifying  potential  interested
companies to  work for).  The TUM will  contribute with  enlisting the
Berkeley visitors onto its IKOM (job fair) program of visits to industries.

\subsection{Contribution to European excellence and European competitiveness}
Applicant's  research experience  will  bring to  Berkeley and back  to TUM 
a clear scientific  competence. There are few competences of  that kind in 
Europe that, at  the same time, help to preserve  from the ``Brain Drain''.  
With applicant's additional contacts, the applicant will help to
solidify  other projects  ideas of  the  IAS group and  of the  Computer
Science Faculty  to   answer  the   interests  of  European   companies  (main
partners in this field are: Kuka Roboter GmbH, The Source
Works, Aldebaran  Robotics, Robert Bosch LLC Germany) and  American ones such as 
Willow Garage Inc. and Robert Bosch LLC USA.

\subsection{Benefit of the mobility to the European Research Area} 
As  can be  evinced from  applicant's curriculum  vitae, the applicant  
has  a significant mobility  ability  and  wishes  not  only to  maintain  his  scientific
collaborations  with a  recognized world-leading  research institution
(TUM, Berkeley, University of Tokyo, Stanford, Robert Bosch LLC in Palo
Alto etc.), but also  to use the  scientific and  technological links
that he has in e.g. whole ROS community. For the applicant, it will  be 
a thriving scientific time to work in  the USA and back in Munich as  
the Munich R\&D capital encompasses:   Applied   Science   (i.e.,  4   Institutes   Fraunhofer
Gesellschaft); Fundamental research  (i.e., 12 Max-Planck Institutes);
Aerospace \&  IT (i.e., 8 DLR  Institutes including a new  major one in
Robotics;   Health  and   Environment  (i.e.,   23   Helmholtz  Center
Institutes); Corporate R\&D  (about 20500 employees); IT infrastructure
(i.e., Leibniz  Supercomputing Centre); IT services for  more than 100
000 university  customers; and  Competence Center for  Networks (e.g.,
GEANT2, X-WIN,  etc.).  

The excellent  quality of life in  Munich, its
dense and very  dynamic industrial base and the  excellent airport and
train connections will support  my mobility plans (professional duties
as well as  personal journeys) so that I will in  a best position. The
dominant scientific  language of the IAS group  is English, including
with  administrative staff  that can  make  the link  to the  external
administrations (and with the support  of TUM Dual Career office). The
TUM  has also  strong life-long  learning training  offers (technology
transfer entrepreneurship, business acumen).   The applicant is convinced that this
extraordinary  environment   will  be  beneficial   to  strengthen  his
knowledge, to reinforce his collaboration network, and will allow him to
experience the excitement of working in a new country.

Before coming back to Europe, the applicant will have the chance to explore 
the current EECS research strategy in future emerging fields at Berkeley:
\begin{itemize}
\item Redesign the hardware stack, rethink levels of separation, retool the design industry;
\item New machine architectures: massively parallel, probably stochastic, possibly quantum; and new ways to program them;
\item Redesign the communication stack top-to-bottom: clean slate;
\item Intelligent human-scale robots;
\item Information systems that know everything;
\item Increasing extroversion: engaging with and solving the problems of society.
\end{itemize}
Being a part of this vivid scientific community for two years and bringing back fresh 
scientific views will benefit to the European Research Area.

\subsection{Impact of the proposed outreach activities}
Outreach activities will be conducted on the different levels both at Berkeley
and at TUM. In the first two years of the proposal a demonstration of \ksem\
project will be given at the day of the open door at EECC Department of Berkeley and
in the third year the demonstration will go live at the ``Lange Nacht der Wissenschaften''
event~\footnote{\url{http://en.wikipedia.org/wiki/Long_Night_of_the_Sciences}}.
Furthermore, based on applicant's previous experiences~\footnote{See Reuter's piece about
the personal robots at TUM: 
\url{http://uk.reuters.com/video/2011/06/30/robot-roomies-collaborate-to-cook-breakf?videoId=216643886&videoChannel=4000}} 
it is expected that the project will receive a wide interest among written and televised media.
A very popular resource of publishing research videos and sharing them with the society at large
has become \emph{Youtube}. Berkeley's towel folding robot has for instance attracted over 650000 
views~\footnote{\url{http://www.youtube.com/watch?v=gy5g33S0Gzo}}. To disseminate information about
the Marie Curie schema Mr. Pangercic will in coordination with the respective organization authorities
organize at least two information events. Lastly, to keep the research community informed, the results of 
\ksem\ project will be presented at above mentioned international conference workshops and the summer school planned for
the second year of the project.
 
% \begin{itemize}
% \item Demonstration at Berkeley and in Munich.
% \item Workshops at ICRA, IROS, RSS
% \item \todo{Pieter: Day of the open dooors?}
% \item Applicant's availability for promotion of Marie Curie programs
% \item TUM frequent appearance in media, e.g.\\
% \begin{small} \url{http://uk.reuters.com/video/2011/06/30/robot-roomies-collaborate-to-cook-breakf?videoId=216643886&videoChannel=4000} \end{small}
% \item summer school
% \item Youtube videos
% \end{itemize}
\newpage